The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-02 exp-resurgence.tex
Revise Pham's singularity formula

In \cite{pham}, Pham describes this formula in a slightly different form, integrating the variation of $\nu/df$, instead of differentiating the integral as we do in equation~\ref{eqn:formula-proof}.

@@

{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.

@@

@@

\begin{revised}Initially, the function $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}^\theta_a(\zeta)$. Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}^\theta_a(\zeta)$. At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\ldots]\end{todo}\end{revised}
\end{remark}
\begin{todo}
\begin{corollary}\label{simple-res-thimble}
If $f$ and $\nu$ are polynomials, the function ${\phi}=\fracderiv{-1/2}{\zeta}{\alpha}\iota$ defined in Remark~\ref{rmk:1/2-deriv} has simple resurgent singularities at $\zeta=\beta$, for all $\beta$ roots of $P$ such that $\beta\neq\alpha$.  
\end{corollary}
\begin{proof}
Recall ${\phi}_\alpha$ is the sum of the Borel transform of $z^{1/2}\series{I}_j$, namely 
\[\hat{\phi}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
Then by Pham's result (see \eqref{rmk:Pham formula}) we know 
\[\hat{\iota}_j(\zeta_j)=\frac{(-\zeta_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-\zeta_j)^{-k} + \text{ hol. funct. }\]
hence 
\[\hat{\iota}_j(\zeta)=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\frac{(-s+\alpha_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-s+\alpha_j)^{-k} \, ds + \text{ hol. funct. }\]
\end{proof}
\end{todo}
\begin{remark}\label{rmk:Pham formula}
\begin{todo}[Add critical point index to $\iota$ and $I$?]\end{todo} When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}$ explicitly as 
\begin{equation}\label{eqn:Pham}
(-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
\end{equation}
for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\ell}$ be defined as
\begin{equation*}
\delta^{-\ell}:=\begin{cases}
\frac{\zeta^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \ell\in\mathbb{N}^*\\
& \\
\frac{(-\zeta)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \text{ hol. funct.} & \text{ if } \ell\notin \mathbb{N}^* 
\end{cases}
\end{equation*}
In particular, if $N=1$, the inverse Laplace transform of $I$ has a fractional power singularity of order $1/2$ at the origin, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}. %as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}. \textcolor{magenta}{We expect this result to hold beyond the polynomial case.} We also expect that equation \eqref{eqn:formula-proof} can be generalized to the $N$-dimensional case replacing the $1/2$-derivative with the $N/2$ one. 
\end{remark}
\section{Examples}\label{sec:examples}
%
\subsection{Airy}\label{sec:airy}
%
The Airy equation is
\begin{equation}\label{eqn:airy}
\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0.
\end{equation}
One solution is given by the Airy function,
\[ \Ai(y) = \frac{1}{2\pi i} \int_\gamma \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
where $\gamma$ is a path that comes from $\infty$ at $-60^\circ$ and returns to $\infty$ at $60^\circ$.

>>>>

In \cite{pham}, Pham describes this formula in a slightly different form, integrating the variation of $\nu/df$, instead of differentiating the integral as we do in equation~\eqref{eqn:formula-proof}.

@@

{\iota}_\alpha = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.

@@

\begin{todo}[\textbf{V} Read through, and remove \texttt{revised} if good]\end{todo}\begin{revised}

@@

\begin{revised}Initially, the function $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}^\theta_a(\zeta)$. Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}^\theta_a(\zeta)$. At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\ldots]\end{todo}\end{revised}
\end{remark}
\begin{todo}
\begin{corollary}\label{simple-res-thimble}
If $f$ and $\nu$ are polynomials, the function ${\phi}=\fracderiv{-1/2}{\zeta}{\alpha}\iota$ defined in Remark~\ref{rmk:1/2-deriv} has simple resurgent singularities at $\zeta=\beta$, for all $\beta$ roots of $P$ such that $\beta\neq\alpha$.  
\end{corollary}
\begin{proof}
Recall ${\phi}_\alpha$ is the sum of the Borel transform of $z^{1/2}\series{I}_j$, namely 
\[\hat{\phi}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
Then by Pham's result (see \eqref{rmk:Pham formula}) we know 
\[\hat{\iota}_j(\zeta_j)=\frac{(-\zeta_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-\zeta_j)^{-k} + \text{ hol. funct. }\]
hence 
\[\hat{\iota}_j(\zeta)=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\frac{(-s+\alpha_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-s+\alpha_j)^{-k} \, ds + \text{ hol. funct. }\]
\end{proof}
\end{todo}
\begin{remark}\label{rmk:Pham formula}
When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} gives us an explicit expression for the singularity of the function $\iota_a$ from Lemma~\ref{lem:thimble_proj_formula-proof}. For some coefficients $c_k$ which depend on $f$, $\nu$, and the thimble $\mathcal{C}_a^\theta$, we have
\begin{equation}\label{eqn:Pham}
\iota_a \in (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta_{\zeta, \alpha}^{(-N/2 - k)} + \mathcal{O}_{\zeta = \alpha},
\end{equation}
where the singularities
\begin{equation*}
\delta_{\zeta,\alpha}^{(-\ell)}:=\begin{cases}
\displaystyle\frac{\zeta_\alpha^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta_\alpha)+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell\in\mathbb{N}^*\\
& \\
\displaystyle\frac{(-\zeta_\alpha)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell\notin \mathbb{N}^* \,.
\end{cases}
\end{equation*}
can be seen as fractional derivatives of the Dirac delta distribution. In particular, if $N=1$, the inverse Laplace transform of the function $I_a$ from Equation~\eqref{exp-int} has a singularity of the form $\zeta_\alpha^{1/2}$, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}. %as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}. \textcolor{magenta}{We expect this result to hold beyond the polynomial case.} We also expect that equation \eqref{eqn:formula-proof} can be generalized to the $N$-dimensional case replacing the $1/2$-derivative with the $N/2$ one. 
\end{remark}
\section{Examples}\label{sec:examples}
%
\subsection{Airy}\label{sec:airy}
%
The Airy equation is
\begin{equation}\label{eqn:airy}
\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0.
\end{equation}
One solution is given by the Airy function,
\[ \Ai(y) = \frac{1}{2\pi i} \int_\gamma \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
where $\gamma$ is a path that comes from $\infty$ at $-60^\circ$ and returns to $\infty$ at $60^\circ$.
